---
title: "Machine Learning Project"
author: "Beatriz Del Fiol"
date: "14 de outubro de 2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. You may use any of the other variables to predict with. You should create a report describing how you built your model, how you used cross validation, what you think the expected out of sample error is, and why you made the choices you did. You will also use your prediction model to predict 20 different test cases.

#Getting data set
```{r dataset}
library(data.table)

TrainDataURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
TestDataURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

# Download and clean the datasets
TrainingData <- read.csv(url(TrainDataURL), na.strings=c("NA","#DIV/0!",""))
TestingData <- read.csv(url(TestDataURL), na.strings=c("NA","#DIV/0!",""))

# Check for the datasets dimemsions
dim(TrainingData)
dim(TestingData)

```
#Preparing dataset
```{r data}
# Delete columns with missing values
TrainingData <-TrainingData[,colSums(is.na(TrainingData)) == 0]
TestingData <-TestingData[,colSums(is.na(TestingData)) == 0]

# Delete unused columns
TrainingData <-TrainingData[,-c(1:7)]
TestingData <-TestingData[,-c(1:7)]

# Check for the datasets dimemsions
dim(TrainingData)
dim(TestingData)

```
#Preparing to run models

Load necessary pachages knitr, caret, rpart.plot, rattle, randomForest, corrplot, gbm 
```{r preparing}
library(knitr)
library(caret)
library(rpart)
library(rpart.plot)
library(rattle)
library(randomForest)
library(corrplot)
library(gbm)
library(e1071)
set.seed(321)
```
#Dividing dataset

70% training and 30% test

```{r dividing data set}
PartData <- createDataPartition(TrainingData$classe, p=0.7, list=FALSE)
TrainingSet <- TrainingData[PartData, ]
dim(TrainingSet)
#names(TrainingSet)

TestingSet <- TrainingData[-PartData, ]
dim(TestingSet)
#names(TestingSet)
```
#Correlation matriz
TraingSet and TestingSet

```{r correlation}




```
#Prediction model Building

It will predicting with tree, Bagging, Random Forests, Booting and verify the accuracy.

##a. Random Forests


```{r random forest}
library(randomForest)
set.seed(321)
RFmodel <- randomForest(classe ~., data=TrainingSet, method="class")

# Predicting
prediction1 <- predict(RFmodel, TestingSet, Type="class")

#Testing
confusionMatrix(prediction1, TestingSet$classe)

```
##b. Decision Tree

```{r decision tree}

set.seed(321)
fitDT <- rpart(classe ~ ., data = TrainingSet, method="class")
predictDT <- predict(fitDT, newdata = TestingSet, type="class")
conf_matrixDT <- confusionMatrix(predictDT, TestingSet$classe)
conf_matrixDT

```
##c. Generalized Boosted Model (GBM)

```{r GBM}
library(caret)
set.seed(321)
fitControl <- trainControl(method="repeatedcv", number=5, repeats=1)
GBMmodel <- train(classe ~., data=TrainingSet, method="gbm", trControl=fitControl, verbose=FALSE)

# Predicting
prediction2 <- predict(GBMmodel, TestingSet)

# Testing
confusionMatrix(prediction2, TestingSet$classe)
```
#Test
Since Random Forest was chosen due to the best accuray, we will run the prediction test with the Test data file.
```{r test}
predictTest <- predict(RFmodel, TestingData)
predictTest

```
